An exposition on the propriety of restricted Boltzmann machines

### 2016-06-10 writing/draft.Rmd
updated grid to be more useful and wrote a little

---
title: "An exposition on the propriety of restricted Boltzmann machines"
author: "Andee Kaplan, Stephen Vardeman, Daniel Nordman"
date: "May, 2016"
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    number_sections: yes
bibliography: references/refs.bib
---

@@

source("helpers/functions.R")
```

#Restricted Boltzmann machines

@@

##Joint distribution
Let $\boldsymbol x = \{h_1, \dots, h_H, v_1,\dots,v_V\}$ represent the states of the visible and hidden nodes in an RBM. Then we posit a parametric form for probabilities corresponding to the state of each node taking the value of $1$.

@@

##Connection to Deep Learning
RBMs have risen to prominence in recent years due to their connection to deep learning [see @hinton2006fast, @salakhutdinov2012efficient, or @srivastava2013modeling for examples]. By stacking multiple layers of RBMs in a deep architecture, the method's proponents claim the ability to learn "internal representations that become increasingly complex, which is considered to be a promising way of solving object and speech recognition problems" [@salakhutdinov2009deep, pp. 450]. The stacking is achieved by treating a hidden layer of one RBM as the visible layer in a second RBM, and so on until the desired architecture is created.

#Degeneracy, instability, and uninterpretability... Oh my!
The highly flexible nature of the RBM ($H + V + H V$ parameters) makes three characteristics of model impropriety of particular concern, *degeneracy, instability, and uninterpretability*. In this section we define these characteristics, discuss how to detect them in the RBM, and point out their relationship to one another.

##Near-degeneracy
In Random Graph Model theory, *degeneracy* occurs when there is a disproportionate amount of probability placed on only a few elements of the sample space, $\mathcal{X}$, by the model. @handcock2003assessing define a model to be near degenerate if $\mu(\boldsymbol \theta)$, the mean parametrization on the model parameters, is close to the boundary of the convex hull of $\{t_k(\boldsymbol x): \boldsymbol x \in \mathcal{X}, k = 1, \dots, K\}$, where $t_k(\boldsymbol x), k = 1, \dots, K\}$ is the set of statistics in the neg-potential function $Q(\boldsymbol x)$ from equation \ref{eqn:pmf}. In other words, if random variables in the neg-potential function $Q(\cdot)$, having support set $\mathcal{S}$, have a collective mean $\mu(\boldsymbol \theta)$ close to the boundary of the convex hull of $\mathcal{S}$ then the model is near-degenerate, as defined by @handcock2003assessing.

@@

##Instability
@schweinberger2011instability introduces a related concept, *instability*, which occurs when small changes in the natural parameters result in large changes in probability masses. This can be thought of as excessive sensitivity in the model. @schweinberger2011instability provides the following tool for detecting instability in the a discrete exponential family model.

@@

##Uninterpretability
@kaiser2007statistical defines a measure of model impropriety called *uninterpretability*, which is characterized as due to the existence of dependence, marginal mean-structure no longer being maintained in the model. This measure concerns the difference between model expectations, E$\left[\boldsymbol X | \boldsymbol \theta\right]$, and expectations given independence, E$\left[\boldsymbol X | \emptyset\right ]$. Using this concept of dependence in a model, it is possible to understand what conditions lead to uninterpretability in a model versus those that guarantee interpretable models. In this method, a model is considered without uninterpretability if its expected value is not very different from the same model with assumed independence. The quantities to compare in the RBM case are

@@

#Tiny example
To illustrate the ideas of graph near-degeneracy, instability, and uninterpretability in a RBM, we will consider a the smallest possible toy example that consists of one visible node $v_1$ and one hidden node $h_1$, both binary. A schematic of this model can be found in figure \ref{fig:toymodel}.

@@

##Impropriety three ways

@@

```{r instab, fig.cap="\\label{fig:instab}$\\max\\limits_{\\boldsymbol x_N \\in \\mathcal{X}_N}[Q(\\boldsymbol x_N)]/N$ for various values of $\\boldsymbol \\theta$ for the tiny example model. This quantity is increasing for larger positive values of $\\boldsymbol \\theta$.", fig.height = 4, fig.align='center'}
expand.grid(theta_h1 = seq(-5, 5, length.out = 5),
            theta_v1 = seq(-5, 5, length.out = 5),
            theta_11 = seq(-5, 5, length.out = 31)) %>%
  data.frame() %>%
  group_by(theta_v1, theta_h1, theta_11) %>%
  do(data.frame(q_max = max(possibles %*% t(data.matrix(.))))) %>%
  ungroup() %>%
  mutate(theta_h1 = factor(theta_h1, labels = paste0("theta[h1]==", unique(theta_h1))), 
         theta_v1 = factor(theta_v1, labels = paste0("theta[v1]==", unique(theta_v1)))) %>%
  ggplot() +
  geom_line(aes(theta_11, q_max/2)) +
  facet_grid(theta_h1 ~ theta_v1, labeller = label_parsed) +
  xlab(expression(theta[11])) +
  ylab(expression(frac(max(Q), H + V)))
```

@@

##Data coding to mitigate degeneracy
Multiple encodings of the binary variables are possible. For example, we could allow $\mathcal{H} \subset \{0,1\}^H, \mathcal{V} \subset \{0,1\}^V$, as in the previous sections or we could encode the state of the variables as $\mathcal{H} \subset \{-1,1\}^H, \mathcal{V} \subset \{-1,1\}^V$. This will result in $t(\boldsymbol x) \in \{0,1\}^{H + V + HV}$ or $t(\boldsymbol x) \in \{-1,1\}^{H + V + HV}$ depending on how we encode on and off states in the nodes. To explore the effect of this encoding on the potential near degeneracy of an RBM, we can explore the behavior of the ratio of the volume of the unrestricted convex hull to the restructed convex hull of $\{t(\boldsymbol x)\}$ to determine how much the restriction in our statistics by including the cross product terms incurs.

@@

In addition to the argument that the $\{-1,1\} data encoding mitigates some near-degeneracy it also has the benefit of providing a guaranteed non-degenerate model at $\boldsymbol \theta = \boldsymbol 0 \in \mathbb{R}^{H + V + H*V}$. The proof of this is included in appendix \ref{appendix:center}.

@@

#Exploring manageable examples
```{r degen-data, message=FALSE, warning=FALSE, cache=TRUE}
#reshape data functions
plot_data <- function(res, grid = FALSE) {

@@

  return(plot.data)
}
indep_params <- function(samp, H, V) {
  samp[, (H + V + 1):ncol(samp)] <- 0
  samp
}
max_Q <- function(theta, stats) {
  apply(crossprod(t(stats), theta), 2, max)
}

@@

exp_vals %>%
  group_by(H, V, N, r1, r2) %>%
  do(data.frame(mean_abs_diff = apply(abs(.$indep_exp[[1]] - .$marg_exp[[1]]), 1, mean))) %>%
  group_by(H, V, N, r1, r2) %>%
  summarise(mean_abs_diff = mean(mean_abs_diff)) %>%
  mutate(Hiddens = paste0("Hiddens: ", H), Visibles = paste0("Visibles: ", V)) -> exp_vals_summary

#instability
res %>%
  group_by(H, V, N, r1, r2) %>%
  do(data.frame(LHS = max_Q(t(.$samp[[1]]), .$stat[[1]])/(.$H + .$V))) %>%
  summarise(mean_max_q = mean(LHS)) -> max_q_summary

@@

```{r degen_plots, fig.cap="\\label{fig:degen_plots}A numerical experiment looking at the fraction of models that were near-degenerate for each combination of magnitude of $\\boldsymbol \\theta$ and model size. The thick black line shows the level where the fraction of -near degenerate models is .05.", fig.height=4}
three_ways %>%
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = frac_degen)) +
  geom_contour(aes(x = r1, y = r2, z = frac_degen), colour = "black", bins = 8) +
  geom_contour(aes(x = r1, y = r2, z = frac_degen), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient("Fraction near-degenerate", low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens) +
  xlab(expression(group("||", theta[main], "||"))) +
  ylab(expression(group("||", theta[interaction], "||"))) +
  theme(aspect.ratio = 1)  -> p.degen

three_ways %>%
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = mean_abs_diff)) +
  geom_contour(aes(x = r1, y = r2, z = mean_abs_diff), colour = "black", bins = 8) +
  #geom_contour(aes(x = r1, y = r2, z = mean_abs_diff), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient(expression(group("|", E(group("", bold(X), "|")*bold(theta)) - E(group("", bold(X), "|")*plain(independence)), "|")), low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens) +
  xlab(expression(group("||", theta[main], "||"))) +
  ylab(expression(group("||", theta[interaction], "||"))) +
  theme(aspect.ratio = 1) -> p.exp_diff

three_ways %>%
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = mean_max_q)) +
  geom_contour(aes(x = r1, y = r2, z = mean_max_q), colour = "black", bins = 8) +
  #geom_contour(aes(x = r1, y = r2, z = mean_max_q), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient(expression(frac(max(Q), H + V)), low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens) +
  xlab(expression(group("||", theta[main], "||"))) +
  ylab(expression(group("||", theta[interaction], "||"))) +
  theme(aspect.ratio = 1) -> p.max_q

@@

```{r instab_plots, fig.cap="\\label{fig:instab_plots}A numerical experiment looking at $\\max\\limits_{\\boldsymbol x_N \\in \\mathcal{X}_N}[Q(\\boldsymbol x_N)]/N$ for each combination of magnitude of $\\boldsymbol \\theta$ and model size. As the magnitude of $\\boldsymbol \\theta$ grows, so does the value of this metric.", fig.height=4}
p.max_q
```

@@

```{r split_plots2, warning=FALSE, fig.cap="\\label{fig:split_plots_dist}The fraction near-degenerate for each magnitude of $\\boldsymbol \\theta$ for each model. For each number of visibles in the model, the fraction near-degenerate becomes greater than zero at larger values of $||\\boldsymbol \\theta||$ as $H$ increases and the slope becomes steeper as $H$ increases also.", fig.height=5}
plot_dat_grid %>% 
  mutate(dist = sqrt(r1^2 + r2^2)) %>%
  group_by(dist, H, V) %>%
  summarise(frac_degen = sum(near_hull)/n()) %>%
  mutate(Hiddens = as.character(H), Visibles = paste0("Visibles: ", V)) %>%
  ggplot() +
  geom_point(aes(dist, frac_degen, colour = Hiddens), size = .5) +
  geom_smooth(aes(dist, frac_degen, colour = Hiddens, group = Hiddens)) +
  facet_wrap(~Visibles) +
  ylim(c(0,1)) +
  xlab(expression(paste(group("||", theta, "||"), ", Distance from the origin"))) +
  ylab("Fraction Near-degenerate")
```

@@

>>>>

---
title: "An exposition on the propriety of restricted Boltzmann machines"
author: "Andee Kaplan, Stephen Vardeman, Daniel Nordman"
date: "June, 2016"
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    number_sections: yes
bibliography: references/refs.bib
---

@@

source("helpers/functions.R")
```
#Introduction

#Background

##Restricted Boltzmann machines

@@

###Joint distribution
Let $\boldsymbol x = \{h_1, \dots, h_H, v_1,\dots,v_V\}$ represent the states of the visible and hidden nodes in an RBM. Then we posit a parametric form for probabilities corresponding to the state of each node taking the value of $1$.

@@

###Connection to Deep Learning
RBMs have risen to prominence in recent years due to their connection to deep learning [see @hinton2006fast, @salakhutdinov2012efficient, or @srivastava2013modeling for examples]. By stacking multiple layers of RBMs in a deep architecture, the method's proponents claim the ability to learn "internal representations that become increasingly complex, which is considered to be a promising way of solving object and speech recognition problems" [@salakhutdinov2009deep, pp. 450]. The stacking is achieved by treating a hidden layer of one RBM as the visible layer in a second RBM, and so on until the desired architecture is created.

##Degeneracy, instability, and uninterpretability... Oh my!
The highly flexible nature of the RBM ($H + V + H V$ parameters) makes three characteristics of model impropriety of particular concern, *degeneracy, instability, and uninterpretability*. In this section we define these characteristics, discuss how to detect them in the RBM, and point out their relationship to one another.

###Near-degeneracy
In Random Graph Model theory, *degeneracy* occurs when there is a disproportionate amount of probability placed on only a few elements of the sample space, $\mathcal{X}$, by the model. @handcock2003assessing define a model to be near degenerate if $\mu(\boldsymbol \theta)$, the mean parametrization on the model parameters, is close to the boundary of the convex hull of $\{t_k(\boldsymbol x): \boldsymbol x \in \mathcal{X}, k = 1, \dots, K\}$, where $t_k(\boldsymbol x), k = 1, \dots, K\}$ is the set of statistics in the neg-potential function $Q(\boldsymbol x)$ from equation \ref{eqn:pmf}. In other words, if random variables in the neg-potential function $Q(\cdot)$, having support set $\mathcal{S}$, have a collective mean $\mu(\boldsymbol \theta)$ close to the boundary of the convex hull of $\mathcal{S}$ then the model is near-degenerate, as defined by @handcock2003assessing.

@@

###Instability
@schweinberger2011instability introduces a related concept, *instability*, which occurs when small changes in the natural parameters result in large changes in probability masses. This can be thought of as excessive sensitivity in the model. @schweinberger2011instability provides the following tool for detecting instability in the a discrete exponential family model.

@@

###Uninterpretability
@kaiser2007statistical defines a measure of model impropriety called *uninterpretability*, which is characterized as due to the existence of dependence, marginal mean-structure no longer being maintained in the model. This measure concerns the difference between model expectations, E$\left[\boldsymbol X | \boldsymbol \theta\right]$, and expectations given independence, E$\left[\boldsymbol X | \emptyset\right ]$. Using this concept of dependence in a model, it is possible to understand what conditions lead to uninterpretability in a model versus those that guarantee interpretable models. In this method, a model is considered without uninterpretability if its expected value is not very different from the same model with assumed independence. The quantities to compare in the RBM case are

@@

#Characterizations
##Tiny example
To illustrate the ideas of graph near-degeneracy, instability, and uninterpretability in a RBM, we will consider a the smallest possible toy example that consists of one visible node $v_1$ and one hidden node $h_1$, both binary. A schematic of this model can be found in figure \ref{fig:toymodel}.

@@

###Impropriety three ways

@@

```{r instab, fig.cap="\\label{fig:instab}$(\\max\\limits_{\\boldsymbol x_N \\in \\mathcal{X}_N}[Q(\\boldsymbol x_N)] - \\min\\limits_{\\boldsymbol x_N \\in \\mathcal{X}_N}[Q(\\boldsymbol x_N)])/N$ for various values of $\\boldsymbol \\theta$ for the tiny example model. This quantity is increasing for larger positive values of $\\boldsymbol \\theta$.", fig.height = 4, fig.align='center'}
expand.grid(theta_h1 = seq(-5, 5, length.out = 5),
            theta_v1 = seq(-5, 5, length.out = 5),
            theta_11 = seq(-5, 5, length.out = 31)) %>%
  data.frame() %>%
  group_by(theta_v1, theta_h1, theta_11) %>%
  do(data.frame(q_max = max(possibles %*% t(data.matrix(.))) - min(possibles %*% t(data.matrix(.))))) %>%
  ungroup() %>%
  mutate(theta_h1 = factor(theta_h1, labels = paste0("theta[h1]==", unique(theta_h1))), 
         theta_v1 = factor(theta_v1, labels = paste0("theta[v1]==", unique(theta_v1)))) %>%
  ggplot() +
  geom_line(aes(theta_11, q_max/2)) +
  facet_grid(theta_h1 ~ theta_v1, labeller = label_parsed) +
  xlab(expression(theta[11])) +
  ylab(expression(frac(max(Q) - min(Q), H + V)))
```

@@

###Data coding to mitigate degeneracy
Multiple encodings of the binary variables are possible. For example, we could allow $\mathcal{H} \subset \{0,1\}^H, \mathcal{V} \subset \{0,1\}^V$, as in the previous sections or we could encode the state of the variables as $\mathcal{H} \subset \{-1,1\}^H, \mathcal{V} \subset \{-1,1\}^V$. This will result in $t(\boldsymbol x) \in \{0,1\}^{H + V + HV}$ or $t(\boldsymbol x) \in \{-1,1\}^{H + V + HV}$ depending on how we encode on and off states in the nodes. To explore the effect of this encoding on the potential near degeneracy of an RBM, we can explore the behavior of the ratio of the volume of the unrestricted convex hull to the restructed convex hull of $\{t(\boldsymbol x)\}$ to determine how much the restriction in our statistics by including the cross product terms incurs.

@@

In addition to the argument that the $\{-1,1\}$ data encoding mitigates some near-degeneracy it also has the benefit of providing a guaranteed non-degenerate model at $\boldsymbol \theta = \boldsymbol 0 \in \mathbb{R}^{H + V + H*V}$. The proof of this is included in appendix \ref{appendix:center}.

@@

##Exploring manageable examples
```{r degen-data, message=FALSE, warning=FALSE, cache=TRUE}
#reshape data functions
plot_data <- function(res, grid = FALSE) {

@@

  return(plot.data)
}
indep_params <- function(samp, H, V) {
  samp[, (H + V + 1):ncol(samp)] <- 0
  samp
}
max_Q <- function(theta, stats) {
  apply(crossprod(t(stats), theta), 2, max)
}
min_Q <- function(theta, stats) {
  apply(crossprod(t(stats), theta), 2, min)
}
min_max_Q <- function(theta, stats) {
  require(dplyr)
  tcrossprod(stats, theta) %>% data.frame() %>%
    cbind(stats) %>%
    group_by_(.dots = colnames(stats)[grepl("v", colnames(stats)) & !grepl("theta", colnames(stats))]) %>%
    summarise_each(funs(max), contains("X")) %>%
    ungroup() %>%
    summarise_each(funs(min), contains("X")) %>%
    select(contains("X")) %>%
    data.matrix() %>%
    t()
}

@@

exp_vals %>%
  group_by(H, V, N, r1, r2) %>%
  do(data.frame(max_abs_diff = apply(abs(.$indep_exp[[1]] - .$marg_exp[[1]]), 1, max))) %>%
  group_by(H, V, N, r1, r2) %>%
  summarise(max_abs_diff = mean(max_abs_diff)) %>%
  mutate(Hiddens = paste0("Hiddens: ", H), Visibles = paste0("Visibles: ", V)) -> exp_vals_summary

#instability
res %>%
  group_by(H, V, N, r1, r2) %>%
  do(data.frame(max = max_Q(t(.$samp[[1]]), .$stat[[1]]),
                min = min_Q(t(.$samp[[1]]), .$stat[[1]]),
                min_max = min_max_Q(.$samp[[1]], .$stat[[1]]))) %>%
  ungroup() %>% 
  group_by(H, V, N, r1, r2) %>%
  mutate(LHS1 = (max - min)/N,
         LHS2 = (max - min_max - H*log(2))/N) %>%
  summarise_each(funs(mean), LHS1, LHS2) -> max_q_summary

@@

```{r degen_plots, fig.cap="\\label{fig:degen_plots}A numerical experiment looking at the fraction of models that were near-degenerate for each combination of magnitude of $\\boldsymbol \\theta$ and model size. The thick black line shows the level where the fraction of -near degenerate models is .05.", fig.height=4}
three_ways %>%
  mutate(r1 = round(r1/(H + V), 8), r2 = round(r2/(H * V), 8)) %>% 
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = frac_degen)) +
  geom_contour(aes(x = r1, y = r2, z = frac_degen), colour = "black", bins = 8) +
  geom_contour(aes(x = r1, y = r2, z = frac_degen), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient("Fraction near-degenerate", low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens) +
  xlab(expression(paste(group("||", theta[main], "||"), "/(H + V)"))) +
  ylab(expression(paste(group("||", theta[interaction], "||"), "/(H*V)"))) +
  theme(aspect.ratio = 1) -> p.degen

three_ways %>%
  mutate(r1 = round(r1/(H + V), 8), r2 = round(r2/(H * V), 8)) %>% 
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = max_abs_diff)) +
  geom_contour(aes(x = r1, y = r2, z = max_abs_diff), colour = "black", bins = 8) +
  #geom_contour(aes(x = r1, y = r2, z = mean_abs_diff), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient(expression(group("|", E(group("", bold(X), "|")*bold(theta)) - E(group("", bold(X), "|")*plain(independence)), "|")), low = "yellow", high = "red", limits = c(0,2)) +
  facet_grid(Visibles~Hiddens) +
  xlab(expression(paste(group("||", theta[main], "||"), "/(H + V)"))) +
  ylab(expression(paste(group("||", theta[interaction], "||"), "/(H*V)"))) +
  theme(aspect.ratio = 1) -> p.exp_diff

three_ways %>%
  mutate(r1 = round(r1/(H + V), 8), r2 = round(r2/(H * V), 8)) %>% 
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = LHS1)) +
  geom_contour(aes(x = r1, y = r2, z = LHS1), colour = "black", bins = 8) +
  #geom_contour(aes(x = r1, y = r2, z = mean_max_q), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient(expression(frac(max(Q) - min(Q), H + V)), low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens) +
  xlab(expression(paste(group("||", theta[main], "||"), "/(H + V)"))) +
  ylab(expression(paste(group("||", theta[interaction], "||"), "/(H*V)"))) +
  theme(aspect.ratio = 1) -> p.max_q

three_ways %>%
  mutate(r1 = round(r1/(H + V), 8), r2 = round(r2/(H * V), 8)) %>% 
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = LHS2)) +
  geom_contour(aes(x = r1, y = r2, z = LHS2), colour = "black", bins = 8) +
  #geom_contour(aes(x = r1, y = r2, z = mean_max_q), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient(expression(frac(max(Q) - min[v](max[h](Q)) - Hlog(2), H + V)), low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens) +
  xlab(expression(paste(group("||", theta[main], "||"), "/(H + V)"))) +
  ylab(expression(paste(group("||", theta[interaction], "||"), "/(H*V)"))) +
  theme(aspect.ratio = 1) -> p.min_max_q

@@

```{r instab_plots, fig.cap="\\label{fig:instab_plots}A numerical experiment looking at $(\\max\\limits_{\\boldsymbol x_N \\in \\mathcal{X}_N}[Q(\\boldsymbol x_N)] - \\min\\limits_{\\boldsymbol x_N \\in \\mathcal{X}_N}[Q(\\boldsymbol x_N)])/N$ for each combination of magnitude of $\\boldsymbol \\theta$ and model size. As the magnitude of $\\boldsymbol \\theta$ grows, so does the value of this metric.", fig.height=4}
p.max_q
```

```{r instab_plots_2, fig.cap="\\label{fig:instab_plots}A numerical experiment looking at $(\\max\\limits_{\\boldsymbol x_N \\in \\mathcal{X}_N}[Q(\\boldsymbol x_N)] - \\min\\limits_{\\boldsymbol v} \\max\\limits_{\\boldsymbol h}[Q(\\boldsymbol x_N)] - H\\log(2))/N$ for each combination of magnitude of $\\boldsymbol \\theta$ and model size. As the magnitude of $\\boldsymbol \\theta$ grows, so does the value of this metric.", fig.height=4}
p.min_max_q
```

@@

```{r split_plots2, warning=FALSE, fig.cap="\\label{fig:split_plots_dist}The fraction near-degenerate for each magnitude of $\\boldsymbol \\theta$ for each model. For each number of visibles in the model, the fraction near-degenerate becomes greater than zero at larger values of $||\\boldsymbol \\theta||$ as $H$ increases and the slope becomes steeper as $H$ increases also.", fig.height=5}
plot_dat_grid %>% 
  mutate(dist = sqrt(r1^2 + r2^2)/(H + V + H*V)) %>%
  group_by(dist, H, V) %>%
  summarise(frac_degen = sum(near_hull)/n()) %>%
  mutate(Hiddens = as.character(H), Visibles = paste0("Visibles: ", V)) %>%
  ggplot() +
  geom_point(aes(dist, frac_degen, colour = Hiddens), size = .5) +
  #geom_smooth(aes(dist, frac_degen, colour = Hiddens, group = Hiddens)) +
  facet_wrap(~Visibles) +
  ylim(c(0,1)) +
  xlab(expression(paste(group("||", theta, "||"), "/(H + V + H*V), Average distance from the origin"))) +
  ylab("Fraction Near-degenerate")
```

@@

#Discussion

#Appendix
